European or American? A re-examination of the transatlantic influence over the IMF

### 2025-05-18 manuscript/manuscript.qmd
Rename dissertation.qmd to manuscript.qmd

---
title: European or American? A re-examination of the transatlantic influence over the IMF
# subtitle: GV499 Dissertation
date: last-modified
authors:
  - name: Dianyi Yang
    email: d.yang17@lse.ac.uk
    orcid: 0009-0004-4652-3429
    correspondence: true
format:
  #native: default
  #docx: default
  orcid-pdf:
    keep-tex: true
    number-sections: true
abstract: This is an abstract.
keywords: IMF, US hegemony, Europe
---

@@

This dissertation therefore attempts to quantitatively compare the influence of the US and Europe on the IMF.

The structure of this dissertation is as follows: @sec-litreview provides a review over the literature on the influence of the US and Europe over the IMF.

>>>>

---
title: European or American? A re-examination of the transatlantic influence over the IMF
date: last-modified
authors:
  - name: Dianyi Yang
    email: d.yang17@lse.ac.uk
    orcid: 0009-0004-4652-3429
    correspondence: true
format:
  #native: default
  #docx: default
  orcid-pdf:
    keep-tex: true
    number-sections: true
abstract: This is an abstract.
keywords: IMF, US hegemony, Europe
---

@@

This paper therefore attempts to quantitatively compare the influence of the US and Europe on the IMF.

The structure of this paper is as follows: @sec-litreview provides a review over the literature on the influence of the US and Europe over the IMF.
